Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

Over the last several decades advances in computing, imaging, and
cyberinfrastructure have supported the growth of digital natural history collections; thus supporting the trends towards open scienc.
In the U.S., programs, such as the National Science Foundation’s former
Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of
data and images for millions of biological specimens. These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
due to both image quality and metadata issues.
% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)

@@

\begin{table}[t]
    \centering
    \caption{Metadata properties}
    \label{tab:properties}
    \begin{tabular}{cccp{0.5\linewidth}}
        \toprule
        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
        \midrule
        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
        \verb|clock_value| & Per Fish & Integer & A fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish. If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
      \bottomrule
\end{tabular}
\end{table}

>>>>

Over the last several decades advances in computing and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-better to say hundreds of thousands, or is millions appropriate?} of biological specimens. These resources are globally available through a range of open access repositories, enabling esearchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
due to both image quality and metadata issues.
% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)

@@

\begin{table*}[t]
    \centering
    \caption{Metadata properties}
    \label{tab:properties}
    \begin{tabular}{cccp{0.5\linewidth}}
        \toprule
        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
        \midrule
        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
        \verb|clock_value| & Per Fish & Integer & A fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish. If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
      \bottomrule
\end{tabular}
\end{table*}
